---
title: "Drydown - Fluxes"
output: github_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo=FALSE,message=FALSE,warning=FALSE,
                      collapse = TRUE,
                      comment = "#>", 
                      fig.path = "images-markdown-picarro/"
                      )
library(here)
source(here::here("code/0-drydown_functions.R"))
theme_set(theme_bw())
```

CO2 concentrations and/or fluxes from the Picarro and EGM-4.  




```{r picarro_files}
picarro_cpcrw = read.csv(here::here("data/processed/picarro_processed_cpcrw.csv.gz"))

picarro_cpcrw2 = 
    picarro_cpcrw %>% 
    dplyr::mutate(DATETIME2 = ymd_hms(DATETIME)) %>% 
    group_by(Core) %>% 
    dplyr::mutate(elapsed_days = as.double(difftime(DATETIME2, min(DATETIME2), units = "days")),
                  Treatment = factor(Treatment, levels = c("drydown", "drought", "sat", "sat_incubation")) 
)

picarro_sr = read.csv(here::here("data/processed/picarro_processed_sr.csv.gz"))

picarro_sr2 = 
    picarro_sr %>% 
    dplyr::mutate(DATETIME2 = ymd_hms(DATETIME)) %>% 
    group_by(Core) %>% 
    dplyr::mutate(elapsed_days = as.double(difftime(DATETIME2, min(DATETIME2), units = "days")),
                  Treatment = factor(Treatment, levels = c("initial", "drydown", "drought", "sat", "sat_incubation")))
```


# 1. PICARRO DATA -- CPCRW

```{r, fig.width=10}
ggplot(picarro_cpcrw2, aes(Treatment, flux_co2_umol_g_s*1000, color = Core_assignment)) + 
    geom_jitter() +
    ylab("flux_co2_nmol_g_s")+
    facet_grid(drying~length, scale = "free_x")+
    geom_hline(yintercept = 0)+
    theme(legend.position="none")
```


<details>
  <summary>time-series by treatment</summary>

```{r cpcrw_co2_flux_trt}
ggplot(picarro_cpcrw2, aes(elapsed_days, flux_co2_umol_g_s*1000, color = Core_assignment)) + 
    geom_point() + geom_line() +
    ylab("flux_co2_nmol_g_s")+
    facet_grid(drying~length, scale = "free_x")+
    geom_hline(yintercept = 0)+
    theme(legend.position="none")
```

```{r cpcrw__co2_flux_trt2}
ggplot(picarro_cpcrw2, aes(DATETIME2, flux_co2_umol_g_s*1000, color = Core_assignment)) + 
    geom_point() + geom_line() +
    ylab("flux_co2_nmol_g_s")+
    facet_grid(drying~length)+
    geom_hline(yintercept = 0)+
    theme(legend.position="none")+
    theme(axis.text.x = element_text(angle = 90))

```
</details>


<details>
  <summary>individual cores</summary>
  
```{r cpcrw_co2_flux_cores}
ggplot(picarro_cpcrw2, aes(elapsed_days, flux_co2_umol_g_s*1000, color = Core_assignment)) + 
    geom_point() + geom_line() +
    ylab("flux_co2_nmol_g_s")+
    facet_wrap(~Core_assignment)+
    #facet_grid(drying~length, scale = "free_x")+
    geom_hline(yintercept = 0)+
    theme(legend.position="none")
```

```{r cpcrw_co2_flux_cores2}
ggplot(picarro_cpcrw2, aes(elapsed_days, flux_co2_umol_g_s*1000, color = Treatment)) + 
    geom_point() + geom_line() +
    ylab("flux_co2_nmol_g_s")+
    facet_wrap(~Core_assignment)+
    #facet_grid(drying~length, scale = "free_x")+
    geom_hline(yintercept = 0)+
    theme(legend.position="top")
```

</details>


### tables -- by core
(hidden)
```{r, include=F}
#CO2: nmol_g_s
picarro_cpcrw2 %>% 
    group_by(Core, Core_assignment, drying, length, Treatment) %>%
    dplyr::summarise(CO2_nmol_g_s = mean(flux_co2_umol_g_s)*1000) %>% 
    ungroup() %>% 
    dplyr::mutate(Treatment = factor(Treatment, levels = c("drydown", "drought", "sat", "sat_incubation"))) %>% 
    spread(Treatment, CO2_nmol_g_s) %>% 
    arrange(length, drying, Core) %>% 
    knitr::kable()
```

### tables -- by treatment
CO2: nmol_g_s
```{r}
picarro_cpcrw2 %>% 
    group_by(Core, Core_assignment, drying, length, Treatment) %>%
    dplyr::summarise(CO2_nmol_g_s = mean(flux_co2_umol_g_s)*1000) %>% 
    ungroup() %>% 
    group_by(drying, length, Treatment) %>%
    dplyr::summarise(CO2_nmol_g_s = mean(CO2_nmol_g_s)) %>% 
    dplyr::mutate(Treatment = factor(Treatment, levels = c("initial","drydown", "drought", "sat", "sat_incubation"))) %>% 
    spread(Treatment, CO2_nmol_g_s) %>% 
    arrange(length, drying) %>% 
    knitr::kable()
```




# 2. PICARRO DATA -- SR

```{r, fig.width=10}
ggplot(picarro_sr2, aes(Treatment, flux_co2_umol_g_s*1000, color = Core_assignment)) + 
    geom_jitter()+
    ylab("flux_co2_nmol_g_s")+
    facet_grid(drying~length, scale = "free_x")+
    geom_hline(yintercept = 0)+
    theme(legend.position="none")
```

<details>
  <summary>time-series by treatment</summary>
  
```{r sr_co2_flux_trt}
ggplot(picarro_sr2, aes(elapsed_days, flux_co2_umol_g_s*1000, color = Core_assignment)) + 
    geom_point() + geom_line() +
    ylab("flux_co2_nmol_g_s")+
    facet_grid(drying~length, scale = "free_x")+
    geom_hline(yintercept = 0)+
    theme(legend.position="none")
```

```{r sr_co2_flux_trt2}
ggplot(picarro_sr2, aes(DATETIME2, flux_co2_umol_g_s*1000, color = Core_assignment)) + 
    geom_point() + geom_line() +
    ylab("flux_co2_nmol_g_s")+
    facet_grid(drying~length)+
    geom_hline(yintercept = 0)+
    theme(legend.position="none")+
    theme(axis.text.x = element_text(angle = 90))
```

</details>

<details>
  <summary>individual cores</summary>

```{r sr_co2_flux_cores}
ggplot(picarro_sr2, aes(elapsed_days, flux_co2_umol_g_s*1000, color = Core_assignment)) + 
    geom_point() + geom_line() +
    ylab("flux_co2_nmol_g_s")+
    facet_wrap(~Core_assignment)+
    #facet_grid(drying~length, scale = "free_x")+
    geom_hline(yintercept = 0)+
    theme(legend.position="none")
```

```{r sr_co2_flux_cores2}
ggplot(picarro_sr2, aes(elapsed_days, flux_co2_umol_g_s*1000, color = Treatment)) + 
    geom_point() +
    ylab("flux_co2_nmol_g_s")+
    facet_wrap(~Core_assignment)+
    #facet_grid(drying~length, scale = "free_x")+
    geom_hline(yintercept = 0)+
    theme(legend.position="top")
```

</details>




### tables -- by core
(hidden)

```{r, include=F}
#CO2: nmol_g_s
picarro_sr2 %>% 
    group_by(Core, Core_assignment, drying, length, Treatment) %>%
    dplyr::summarise(CO2_nmol_g_s = mean(flux_co2_umol_g_s)*1000) %>% 
    ungroup() %>% 
   # dplyr::mutate(Treatment = factor(Treatment, levels = c("drydown", "drought", "sat", "sat_incubation"))) %>% 
    spread(Treatment, CO2_nmol_g_s) %>% 
    arrange(length, drying, Core) %>% 
    knitr::kable()
```

### tables -- by treatment
CO2: nmol_g_s
```{r}
picarro_sr2 %>% 
    group_by(Core, Core_assignment, drying, length, Treatment) %>%
    dplyr::summarise(CO2_nmol_g_s = mean(flux_co2_umol_g_s)*1000) %>% 
    ungroup() %>% 
    group_by(drying, length, Treatment) %>%
    dplyr::summarise(CO2_nmol_g_s = mean(CO2_nmol_g_s, na.rm = T)) %>% 
   # dplyr::mutate(Treatment = factor(Treatment, levels = c("drydown", "drought", "sat", "sat_incubation"))) %>% 
    spread(Treatment, CO2_nmol_g_s) %>% 
    arrange(length, drying) %>% 
    knitr::kable()
```


---

# 3. EGM DATA -- CO2 concentrations

```{r egm_files}
egm = read.csv(here::here("data/processed/egm_concentrations.csv")) %>% 
    mutate(date = as.Date(date))
```

## ambient CO2
```{r egm_ambient}
egm %>% 
    filter(Core %in% c("AMB", "amb")) %>% 
    ggplot(aes(x = date, y = PPM_CO2))+
    geom_point()+
    labs(title = "ambient CO2")+
    theme_bw()+
    NULL
```

## all cores

```{r egm_cores, include=F}
egm %>% 
  filter(Site=="CPCRW") %>% 
  ggplot(aes(x = date, y = PPM_CO2, color = Core))+
  geom_point()+ geom_path()+
  labs(title = "CPCRW all cores",
       subtitle = "not normalized to core wt")+
  theme_bw()+
  ylim(450, 1200)+
  NULL

egm %>% 
  filter(Site=="SR") %>% 
  ggplot(aes(x = date, y = PPM_CO2, color = Core))+
  geom_point()+ geom_path()+
  labs(title = "SR all cores",
       subtitle = "not normalized to core wt")+
  theme_bw()+
  ylim(450, 1200)+
  NULL
```

```{r egm_cores_mass}
egm %>% 
  filter(Site=="CPCRW") %>% 
  ggplot(aes(x = date, y = CO2_ppm_g, color = Core))+
  geom_point()+ geom_path()+
  labs(title = "CPCRW all cores",
       subtitle = "normalized to core wt")+
  theme_bw()+
  NULL

egm %>% 
  filter(Site=="SR") %>% 
  ggplot(aes(x = date, y = CO2_ppm_g, color = Core))+
  geom_point()+ geom_path()+
  labs(title = "SR all cores",
       subtitle = "normalized to core wt")+
  theme_bw()+
  NULL
```



---
<details>
    <summary>Session Info</summary>

Date Run: `r Sys.Date()`

```{r sessioninfo}
sessionInfo()
```
    
</details>

--- 

# PICARRO CONCENTRATIONS

```{r picarro_ppm_cpcrw, fig.height = 7, fig.width=12}
corekey = read.csv(COREKEY)
picarro_cpcrw_ppm = read.csv("data/processed/picarro_processed_ppm_ccprw.csv.gz")

picarro_cpcrw_ppm2 = 
  picarro_cpcrw_ppm %>% 
  filter(Core != 0) %>% 
  mutate(coreID = paste0("C",Core)) %>% 
  dplyr::select(-Core) %>% 
  dplyr::mutate(DATETIME2 = ymd_hms(DATETIME)) %>% 
  group_by(coreID) %>% 
  dplyr::mutate(elapsed_days = as.double(difftime(DATETIME2, min(DATETIME2), units = "days")),
                Treatment = factor(Treatment, levels = c("drydown", "drought", "sat", "sat_incubation")) 
  ) %>% 
  filter(CO2_dry > 0) %>% 
  filter(length %in% c("30 day", "90 day", "150 day")) %>% 
  mutate(length = factor(length, levels = c("30 day", "90 day", "150 day")))



ggplot(picarro_cpcrw_ppm2, aes(Treatment, CO2_dry, color = Core_assignment)) + 
  geom_jitter(size = 0.5) +
  facet_grid(drying~length, scale = "free_x")+
  geom_hline(yintercept = 0)+
  theme(legend.position="none")

ggplot(picarro_cpcrw_ppm2, aes(Treatment, CO2_dry, color = Core_assignment)) + 
  geom_point(aes(group = coreID), position = position_dodge(width = 0.7), size = 0.5) +
  facet_grid(drying~length, scale = "free_x")+
  geom_hline(yintercept = 0)+
  theme(legend.position="none")+
  ylim(0, 6000)+
  labs(x = "",
       y = "CO2 (ppm)",
       title = "CPCRW")
```

```{r}
  picarro_cpcrw_ppm %>% 
  filter(Core == 0) %>% 
    ggplot(aes(x = as.Date(DATETIME), y = CO2_dry))+
    geom_point()+
    labs(title = "ambient CO2 by Picarro")
```

```{r picarro_ppm_sr, fig.height = 7, fig.width=12}
picarro_sr_ppm = read.csv("data/processed/respiration/picarro_processed_ppm_sr.csv.gz") %>% mutate_all(na_if,"")


picarro_sr_ppm2 = 
  picarro_sr_ppm %>% 
  filter(Core != 0) %>% 
  mutate(coreID = paste0("S",Core)) %>% 
  dplyr::select(-Core) %>% 
  dplyr::mutate(DATETIME2 = ymd_hms(DATETIME)) %>% 
  group_by(coreID) %>% 
  dplyr::mutate(elapsed_days = as.double(difftime(DATETIME2, min(DATETIME2), units = "days")),
                Treatment = factor(Treatment, levels = c("initial", "drydown", "drought", "sat", "sat_incubation")) 
  ) %>% 
  filter(CO2_dry > 0) %>% 
  filter(length %in% c("30 day", "90 day", "150 day")) %>% 
  mutate(length = factor(length, levels = c("30 day", "90 day", "150 day")))

ggplot(picarro_sr_ppm2 %>% filter(!is.na(drying)), aes(Treatment, CO2_dry, color = Core_assignment)) + 
  geom_jitter(size = 0.5) +
  facet_grid(drying~length, scale = "free_x")+
  geom_hline(yintercept = 0)+
  theme(legend.position="none")

ggplot(picarro_sr_ppm2 , aes(Treatment, CO2_dry, color = Core_assignment)) + 
  geom_point(aes(group = coreID), position = position_dodge(width = 0.7), size = 0.5) +
  facet_grid(drying~length, )+
  geom_hline(yintercept = 0)+
  theme(legend.position="none")+
  ylim(0, 6000)+
  labs(x = "",
       y = "CO2 (ppm)",
       title = "SR")

```

