---
title: "NMR"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      collapse = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      comment = "#>",
                      fig.path = ("images-markdown-nmr/"))
library(drake)
```

---

<details>
  <summary>Time Zero -- click to open</summary>


## Time Zero
Time Zero soils had mostly aliphatic groups, with < 15 % aromatic

```{r, fig.width=5}
readd(gg_relabund_barplot)$relabund_bar_timezero
```

#### PERMANOVA
```{r}
readd(nmr_permanova)$permanova_tzero$aov.tab %>% 
  broom::tidy() %>% 
  knitr::kable()
```
For time-zero samples, NMR-based composition did not differ by Site or depth.

</details>

---

<details>
  <summary>Drought Samples - Statistics</summary>
  
In drought-incubated samples, NMR-based composition was significantly influenced by saturation type, Site, and depth. Drought length or drought intensity did not significantly influence WEOC composition.

Saturation type (instant chemistry vs. saturated) accounted for 13 % of total variation (R2 value).

```{r}
readd(nmr_permanova)$permanova_drought$aov.tab %>% 
  broom::tidy() %>% 
  knitr::kable()
```

**0-5cm only**

Saturation type (instant chemistry vs. saturated) accounted for 25 % of total variation (R2 value).  

Site (CPCRW vs. SR) accounted for 5 % of total variation (R2 value).


```{r}
readd(nmr_permanova)$permanova_drought_toponly$aov.tab %>% 
  broom::tidy() %>% 
  knitr::kable()
```





</details>

---

<details>
  <summary>PCA</summary>
  
#### Including Time Zero samples
```{r, fig.height=6, fig.width=6}
readd(gg_pca)$gg_pca_overall1 + theme(legend.position = "right")
```

Time-zero samples had a greater contribution of aliphatic groups. Instant-rewet samples had a greater contribution of aliphatic, alpha-H and amide groups. Saturated soils had a greater contribution of aromatic groups.



#### Only drought samples (no Time Zero)
```{r, fig.height=10, fig.width=10}
readd(gg_pca)$gg_pca_drought
```

</details>

---

<details>
  <summary>Relative abundance bar plots</summary>

```{r, fig.width=7}
readd(gg_relabund_barplot)$relabund_bar_simple
```  
  
  
### All samples  
```{r, fig.width=5}
readd(gg_relabund_barplot)$relabund_bar_timezero
```

```{r, fig.height=12, fig.width=12}
readd(gg_relabund_barplot)$relabund_bar_cores
```

```{r, fig.height=6, fig.width=12}
readd(gg_relabund_barplot)$relabund_bar_top
```
  
</details>

---

<details>
  <summary>NMR Spectra</summary>
```{r, fig.height=7, fig.width=15}
readd(gg_spectra)
```
  
  
</details>

---

---

<details>
  <summary>Session Info</summary>

date run: `r Sys.Date()`

```{r}
sessionInfo()
```


</details>