---
title: "FTICR"
output: html_document
---

This document contains results for FTICR-MS data.  
Click [here](https://github.com/PNNL-TES/TES-drydown/blob/master/markdown/report_fticr_full.md) for a more detailed report, with additional analyses.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      collapse = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      comment = "#>",
                      fig.path = ("images-markdown-fticr/subset/"))

library(drake)
```

---

<details>
  <summary>RESEARCH QUESTIONS -- click to open</summary>

1. effect of drought duration?
1. effect of drought intensity? **CW** (constant weight drying) vs. **FAD** (forced air drying, more intense)
1. effect of post-drought rewetting? instant rewet (no saturation) vs. 2 week saturation
1. difference by site?
1. difference by soil depth? 0-5 cm vs. 5cm-end

</details>

---

<details>
  <summary>TIME ZERO -- click to open</summary>

## TIME ZERO SAMPLES
### Van Krevelen plots
```{r vk_tzero, fig.height=4, fig.width=6}
readd(gg_vk_timezero)
```


There was no significant influence of site, but there was a significant influence of depth (0-5cm vs. 5cm-end).

<details>
  <summary>statistics</summary>
  
#### PCA

```{r pca_tzero}
readd(gg_pca_tzero)
```

#### PERMANOVA
```{r permanova_tzero}
readd(fticr_permanova_tzero)
```

</details>

#### Relative abundance
```{r relabund_tzero}
readd(gg_relabund_bar)$relabund_bar_tzero
```

(ANOVA): 

- aromatic, condensed aromatic influenced by Site and depth
- aliphatic, lignin did not change significantly by Site or depth

</details>

---

<details>
  <summary>STATISTICS -- click to open</summary>

## STATISTICS
### PERMANOVA
```{r permanova}
readd(fticr_permanova)
```

PERMANOVA results for *drought samples only*. i.e. no time zero

- All variables showed a significant influence on WEOC composition. 
- Saturation and depth were the strongest predictors, each accounting for **~28 %** of total variation (see `R2` column). 
- Site, drought length, drought intensity were significant, but each accounted only for 2-3 % of total variation. 

</details>

---

<details>
  <summary>PCA on drought samples -- click to open</summary>
  
## PCA
 
**including time-zero samples**

```{r pca_sat}
readd(gg_pca)$gg_pca_overall1
```

**drought samples only**
```{r pca2}
readd(gg_pca2)
```

</details>

--- 

<details>
  <summary>DROUGHT INTENSITY -- click to open</summary>

## HOW DID DRYING (CW VS. FAD) INFLUENCE CHEMISTRY?

```{r vk_newpeaks_drying2, fig.height=6, fig.width=6}
readd(gg_newpeaks_drying_overall)
```


</details>

---

<details>
  <summary>REWETTING -- click to open</summary>

## HOW DID WETTING (INSTANT REWET VS. SATURATION INCUBATION) INFLUENCE CHEMISTRY?

```{r vk_newpeaks_saturation2, fig.height=6, fig.width=3.5}
readd(gg_newpeaks_saturation_overall)
```

</details>

---


---


<details>
  <summary>SESSION INFO -- click to open</summary>

date run: `r Sys.Date()`

```{r}
sessionInfo()
```

</details>
