---
title: "FTICR"
output: html_document
---

This document contains results for FTICR-MS data.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      collapse = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      comment = "#>",
                      fig.path = ("images-markdown-fticr/"))

library(drake)
```

---

<details>
  <summary>RESEARCH QUESTIONS -- click to open</summary>

1. effect of drought duration?
1. effect of drought intensity? **CW** (constant weight drying) vs. **FAD** (forced air drying, more intense)
1. effect of post-drought rewetting? instant rewet (no saturation) vs. 2 week saturation
1. difference by site?
1. difference by soil depth? 0-5 cm vs. 5cm-end

</details>

---

<details>
  <summary>EXPLORATORY ANALYSIS -- click to open</summary>

## EXPLORATORY ANALYSIS
### Van Krevelen domains
```{r vk_domains, fig.height=5, fig.width=5}
readd(gg_vankrevelen_domains)
```

### Van Krevelen plots by treatment
```{r vk_plots, fig.height=10, fig.width=8}
readd(gg_vankrevelens)$gg_cpcrw_all
readd(gg_vankrevelens)$gg_sr_all
```

### RELATIVE ABUNDANCE

```{r relabund_barplot, fig.height=10, fig.width=10}
readd(gg_relabund_bar)$relabund_bar_trt
```

</details>

---

<details>
  <summary>PCA -- click to open</summary>

## PCA

```{r pca}
readd(gg_pca)
```

</details>

--- 

<details>
  <summary>TIME ZERO -- click to open</summary>

## TIME ZERO SAMPLES
### Van Krevelen plots
```{r vk_tzero}
readd(gg_vk_timezero)
```

### PCA

```{r pca_tzero}
readd(gg_pca_tzero)
```

### PERMANOVA
```{r permanova_tzero}
readd(fticr_permanova_tzero)
```

### Relative abundance
```{r relabund_tzero}
readd(gg_relabund_bar)$relabund_bar_tzero
```


</details>

---

<details>
  <summary>EFFECT OF DROUGHT -- click to open</summary>

## HOW DID DROUGHT SAMPLES COMPARE TO TIME ZERO?
```{r vk_tzero_diff, fig.width=10, fig.height=8}
readd(gg_vk_tzero_diff)
```


</details>

---


<details>
  <summary>DROUGHT INTENSITY -- click to open</summary>

## HOW DID DRYING (CW VS. FAD) INFLUENCE CHEMISTRY?
```{r vk_drying, fig.height= 6, fig.width=8}
readd(gg_vankrevelens)$gg_cpcrw_drying
readd(gg_vankrevelens)$gg_sr_drying
```

```{r vk_newpeaks_drying, fig.height=15, fig.width=10}
readd(gg_vk_newpeaks_drying)
```



</details>

---

<details>
  <summary>REWETTING -- click to open</summary>

## HOW DID WETTING (INSTANT REWET VS. SATURATION INCUBATION) INFLUENCE CHEMISTRY?
```{r vk_newpeaks_saturation, fig.height=10, fig.width=10}
readd(gg_vk_newpeaks_saturation)
```

</details>

---

<details>
  <summary>OXIDATION STATE -- click to open</summary>
  
## NOSC

NOSC by drying
```{r nosc_drying, fig.height=8, fig.width=10}
readd(gg_nosc)$nosc_by_drying
```

NOSC by saturation
```{r nosc_saturation, fig.height=8, fig.width=10}
readd(gg_nosc)$nosc_by_drying
```

</details>

---

<details>
  <summary>STATISTICS -- click to open</summary>

## STATISTICS
### PERMANOVA
```{r permanova}
readd(fticr_permanova)
```


</details>

---

<details>
  <summary>SESSION INFO -- click to open</summary>

date run: `r Sys.Date()`

```{r}
sessionInfo()
```

</details>
